Adopting agile in the large: motivations, success factors and challenges

### 2014-05-19 journal/article.tex
Minor edit

Examples on topics excluded by the first facet are agile manufacturing, and
applying Scrum practices in management boards, as these do not relate to
software engineering. In addition, we required that the organizational
transformation was aimed to introduce agile methods, which excluded other
development methods than agile \cite{Sagesser2013}, and use of agile
methods in other contexts than software development \cite{Hodgkins2007}.

>>>>

Examples on topics excluded by the facet of \emph{agile software development}
are agile manufacturing and applying Scrum practices in management boards, as
these do not relate to software engineering. In addition, we required that the
organizational transformation was aimed to introduce agile methods, which
excluded other development methods than agile \cite{Sagesser2013}, and use of
agile methods in other contexts than software development \cite{Hodgkins2007}.
